A Hitchhiker's Guide to Reproducible Research in R

### 2021-06-14 manuscript.Rmd
what is rmarkdown metadata and how does repro use it

@@

We argue that a preregistration as code (PAC) is an excellent planning tool that offers several benefits over traditional preregistration.
For a PAC, researchers write a reproducible, dynamically generated manuscript including the sections Introduction, Methods, and Results before they gather data.

>>>>

If you made changes to a file you have to stage and then commit these changes.
The easiest way is to use the RStudio Git pane.
You click on the empty box next to the file you want to stage and when a tick appears the file is staged.
After you have staged all files you want click on the commit button, explain curtly why you made those changes in a commit message and then click on commit.

The files you created and the changes you made still have not left your computer.
To backup and share the files, you can publicly upload those changes to GitHub with:

```{r, eval=FALSE}
usethis::use_github()
```

Depending on your computer configuration this may ask to setup a secure connection to GitHub.

If you are not yet ready to share you project publicly use:

```{r, eval=FALSE}
usethis::use_github(private = TRUE)
```

Now that you have created a project that is under version control we turn to dynamic document generation.
Three aspects are important to understand a dynamic document:

1. Text
2. Code
3. Metadata

The text of an R Markdown is written in Markdown.
The following example shows how to signify a header, a bold word and a list in Markdown:

```markdown
<!--this is a Markdown file -->
# Header

Normal text.
Important **word** in bold.

To do list:

* do research
* do more research
* spend time with family
```

Code is separated by three backtics and the programming language in curly braces like here:

````markdown
This is normal text, written in Markdown.

`r ''````{r}
# this is R code
1 + 1
```
````

Now that you know how to write text and R code in an RMarkdown the only thing you need to know about is metadata, like the title or the output format.

Metadata are placed at the beginning of the document and are seperated by three dashes; the following example is a full markdown document where the header is in lines 1-6.

````markdown
---
title: A Hitchhiker's Guide to Reproducible Research in R
author: Aaron Peikert, Caspar J. Van Lissa and Andreas M. Brandmaier
abstract: A paper about recalculating the same thing more than once.
output: html_document
---

Important for reproducibility:

1. Version Control
2. Dynamic Document Creation
3. Dependency Tracking
4. Software Management

`r ''````{r}
# this is R code
t.test(extra ~ group, data = sleep)
```
````

Most of the metadata fields are self explanatory (like the author field) but any package may use the metadata for their purposes.
Often, for example, does a specific output format require more metadata i.e. the `rticles`-package for authoring scientific manuscripts.
RMarkdown was extended to hundreds of document formats which are often highly configurable by their metadata.
The `repro` package uses the metadata, not to change the output, but to make the document more reproducible, simply by listing resources, i.e., scripts, data, and packages, your document depends on.

```markdown
---
title: A Hitchhiker's Guide to Reproducible Research in R
author: Aaron Peikert, Caspar J. Van Lissa and Andreas M. Brandmaier
abstract: A paper about recalculating the same thing more than once.
output: html_document
repro:
  scripts:
    - R/load.R
  data:
    - data/mtcars.csv
  packages:
    - tidyverse
    - usethis
    - gert
---
```

These information make internal dependencies to other files in the project and external dependencies to R packages explicit.
`repro` can use these information to infer a Makefile for the dependencies on other files and a Dockerfile that includes all required packages.
In day-to-day work the simplest solution is to use the function `repro::automate()` which both infers a Makefile and a Dockerfile from all RMarkdown files (all files with the ending `.Rmd`).
Everytime you changed the `repro`-metadata, change the output format, or add a new RMarkdown, the Makefile and Dockerfile are potentially outdated and you should run `repro::automate()` to keep them up to date.
The function `repro::automate()` does not overwrite manual changes and there is no harm in running it too often.

@@

We argue that a preregistration as code (PAC) is an excellent planning tool that offers several benefits over traditional preregistration.
For a PAC, researchers write a reproducible, dynamically generated manuscript including the sections Introduction, Methods, and Results before they gather data using simulated data.
